% !TEX program = xelatex
\documentclass[]{CV}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Szczekulski}{Jan}{Data Scientist/Software Engineer}{\contactline{\href{http://jan-cs.com/}{jan-cs.com}}{\href{https://www.github.com/szczekulskij}{szczekulskij}}{\href{https://www.linkedin.com/in/jan-szczekulski-272ab615a/}{Jan}}{\href{mailto:szczekulskij@gmail.com}{szczekulskij@gmail.com}}{\href{tel:+48604982233}{+48604982233}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.705\textwidth} 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\runsubsection{The Hut Group}
\descript{| Data Scientist Experimentation}
\location{Sept 2020 – Present | Manchester, UK}
\quad
\begin{tightemize}

% -> point 1
\item Improved \& automated A/B testing tools surrounding internal A/B testing such as duration estimation or automated analyses tool. Improved internal backend used for managing experiments.

% -> point 2
\item I led the `experimentable widgets` project, which enabled stakeholders to make changes to site widgets as A/B tests. To do this, I had to look into and make alterations to the larger internal architecture, which included 4 backends and 2 frontends

% -> point 3
\item I conducted 7 A/B/n tests, and performed thorough data analysis. These resulted in £1million rise in sales year-on-year.

% -> point 4
\item Helped develop a company-wide ML algorithm responsible for short-term demand forecasting.

% -> point 5
\item Built data pipelines from scratch, including setting up a virtual machine, Jenkins, and writing Python scripts.

\quad
\end{tightemize}

\vspace{\topsep}
\runsubsection{Ambroziak's Dermatology Clinic}
\descript{| Research Assistant}
\location{2021-present}
\begin{tightemize}

% -> point 1
\item First research focused on identifying the visit frequency at which no more progress can be made in treating Port-Wine-Stain birthmarks, as well as to confirm medical experience that PWS will worsen over time if not treated.
% Analyzed data on long-term treatment of PWS-type birthmarks.  Research revealed that if treatment is discontinued, the condition will worsen. Consequently, this lead to introduction of a novel sustained treatment for PWS.

% -> point 2
% \item I am currently conducting research that aims to use Convolutional Neural Networks (CNNs) to predict the numerical and visual success rate of laser treatment for birthmarks, by leveraging the relationship between the position and colour of the marks and the treatment's effectiveness.
\item The second research studied the effectiveness of Convolutional Neural Networks and Transfer Learning in determining the success rate of treating Port-Wine Stain Birthmark by leveraging the relationship between the position and colour of the marks pre-treatment and the treatment's effectiveness.


\end{tightemize}
\sectionsep

\vspace{\topsep} % Hacky fix for awkward extra vertical space
\runsubsection{University of Liverpool}
\descript{| Research Assistant  }
\location{June 2020 – Aug 2020 | Liverpool, UK}
\location{Aug 2022 – Present | Liverpool, UK}
\begin{tightemize}
% -> point 1
\item This research focused on improving the efficiency of tomography reconstruction by applying classification CNNs to find the best angles to be used for the 3d reconstruction of nanowires based on the sinograms of the nanowire's 2d slices.


\end{tightemize}



\section{Projects}
\runsubsection{Improving DDPG}
\descript{| Python, Numpy,PyTorch}
\location{2020}
\begin{tightemize}

% -> point 1
\item For my thesis I've implemented \& improved stability and convergence of reinforcement learning algorithm DDPG using Stochastic Weighted Average \& One-Cycle methods.

\end{tightemize}

\runsubsection{Monet me this}
\descript{| Python, Numpy, PyTorch}
\location{2022}
\begin{tightemize}

% -> point 1
\item I re-implemented CycleGAN and applied Differential Augmentation, training on Kaggle's Dataset to create a game that tests players' ability to differentiate between authentic paintings created by Claude Monet and AI-generated paintings.

\end{tightemize}
\sectionsep

% \runsubsection{Project 4/5/6 - In Implementation}
% \descript{|Languages (Python, Pytorch etc.)}
% \location{year}
% \begin{tightemize}

% % -> point 1
% \item point1

% % -> point 2
% \item point2

% % -> point 3
% \item point3


% \end{tightemize}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Awards} 
% \begin{tabular}{rll}
% 2020	     & Finalist & Lorem Ipsum\\
% 2018	     & $2^{nd}$ & Dolor Sit Amet\\
% 2015	     & Finalist  & Cras posuere\\
% \\
% \end{tabular}
% \sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.25\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\sectionsep
\location{Proficient:}
Python \textbullet{} SQL \textbullet{} Java \\
\sectionsep
\location{Experienced:}
JavaScript \textbullet{} Shell \\
\sectionsep
\location{Familiar:}
Prolog \textbullet{}  \LaTeX\ \textbullet{} C++ \\
\sectionsep
\sectionsep
\subsection{Frameworks}
\sectionsep
Pandas \textbullet{} PyTorch \& Tensorflow \\  Matplotlib \textbullet{} SpringBoot \textbullet{} React \\
\sectionsep
\sectionsep
\subsection{Tools}
\sectionsep
Git \textbullet{} Jenkins  \\ Docker \textbullet{} Linux(CentOS) \\

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\subsection{University of Liverpool}
\descript{Bachelor's in Computer Science 
\\and Mathematics}
\location{2017 - 2020 | Liverpool, UK}
\location{First Class (Honours)}

\sectionsep
\subsection{Tadeusz Czacki's High School}
\descript{Extended Mathematics, English and Physics}
\location{2014 - 2017 | Warsaw, Poland}
\location{A*AB accordingly}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXTRA-CURRICULAR
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{EXTRA-CURRICULAR} 
\subsection{Table Tennis Club}
\descript{Team Captain}
\descript{Social Welfare Officer}
\location{2018 - 2019 | University of Liverpool, UK}
\sectionsep
\sectionsep

\subsection{Languages}
\descript{Polish}
\descript{English}
\sectionsep
\sectionsep

\subsection{Hobbies}
\descript{Sports}
\location{Basketball, Running \& Martial arts}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\descript{Relaxation}
\location{Dancing, Books \& Guitar}





\end{minipage} 
\end{document}  \documentclass[]{article

