\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Jan Szczekulski} \\ \vspace{3pt}
    \href{mailto:jszczekulski@ucsd.edu}{\raisebox{-0.2\height}\faEnvelope\  \underline{email}} ~ 
    \href{https://jan-cs.com/}{\raisebox{-0.2\height}\faGlobe\ \underline{website}} ~
    \href{https://www.linkedin.com/in/jan-szczekulski-272ab615a}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin}}  ~
    \href{https://github.com/szczekulskij}{\raisebox{-0.2\height}\faGithub\ \underline{github}}
    \vspace{-8pt}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

\resumeSubheading
    {Amazon}{June 2024 -- Sept. 2023}
    {Software Development Engineer Intern}{Seattle, USA}
    \resumeItemListStart
        \resumeItem{Designed and implemented a scalable AWS system (Lambda, AppConfig, ECS), approved by senior engineers, for fulfillment center orchestration, capable of cost-efficiently handling millions calls per day}
      \resumeItemListEnd

\vspace{5pt}
\resumeSubheading
      {Contextual Robotics Institute}{September 2023 -- Present}
      {Graduate Research Assistant}{San Diego, USA}
      \resumeItemListStart
        \resumeItem{Developed a SOTA mobile robot tabletop re-arrangement algorithm; manuscript under review for publication}
      \resumeItemListEnd

\vspace{5pt}
\resumeSubheading
      {The Hut Group}{Dec. 2021 -- Aug. 2023}
      {Full-Stack Software Engineer}{Manchester, UK}
      \resumeItemListStart
        \resumeItem{Led A/B testing widgets project, driving 25 effortless A/B tests and £70 million YoY revenue growth.}
        \resumeItem{Designed and implemented integration of widget-serving, A/B testing, and page-serving backends}
        \resumeItem{Extended internal frontends for seamless and user-friendly setup of widget-based experiments.}
        \resumeItem{Dockerized and Kubernetized internal systems and data pipelines.}
        \resumeItem{Mentored several junior SDEs, accelerating their onboarding and integration into the team.}
    \resumeItemListEnd
    
\vspace{5pt}
\resumeSubheading
      {The Hut Group}{Sept. 2020 -- Dec. 2021}
      {Data Scientist}{Manchester, UK}
      \resumeItemListStart
            \resumeItem{Automated A/B testing tasks, introduced integration testing, and set up CI/CD for multiple tools.}
            \resumeItem{Built data pipelines from scratch, integrating with Jenkins and GitHub Actions.}
            \resumeItem{Managed virtual machines, handling patching, setup, and integration with GitHub/Jenkins.}
        \resumeItemListEnd
        

\resumeSubHeadingListEnd
% \vspace{-16pt}
% \vspace{1pt}

%-----------EDUCATION-----------
\vspace{1pt}
\section{Education}
\vspace{1pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {UC San Diego}{Sept. 2023 -- Dec. 2024}
      {Master of Science in Computer Science}{San Diego, USA}
    \resumeSubheading
      {University of Liverpool}{Sept. 2017 -- May 2020}
      {BSc (honours) in Computer Science and Mathematics}{Liverpool, UK}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
%-----------PROJECTS-----------
\vspace{1pt}
\section{Selected Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading {\textbf{Dropbox Replica} $|$ \emph{Go}}{May 2024}
        \resumeItem{I developed a simplified Dropbox replica for synchronous file syncing between servers and a laptop, implementing RAFT from scratch and using gRPC for communication.}
        
    \resumeProjectHeading {\textbf{Monet-me-this web app} $|$ \emph{React, SpringBoot, Python, PyTorch, Linux}}{November 2022}
        \resumeItem{Developed and deployed an AI-driven web app game where players distinguish between famous painters' works and images generated by CycleGAN AI.}
        \vspace{1pt}

    \resumeProjectHeading {\textbf{AI application in medicine} $|$ \emph{React, SpringBoot, Python, PyTorch, Linux}}{November 2022}
        \resumeItem{In collaboration with Lazarski University, used transfer learning, Google's Dermatology Embedding API, and CycleGAN to predict Port-Wine Stain treatment outcomes from pre-op photos. Orally presented the research at medical conferences in Phoenix and Baltimore}
      
    \resumeSubHeadingListEnd
% \vspace{-15pt}
\vspace{5pt}

\vspace{5pt}



%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Go, SQL, graphQL, TypeScript, HTML/CSS, Python, Shell} \\
     \textbf{Frameworks}{: SpringBoot, Django, React, AngularJS, Pandas, Matplotlib, PyTorch} \\
     \textbf{Technologies/Tools}{:Docker, Jenkins, Kubernetes, Github actions, } \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Publications}
    \resumeSubHeadingListStart
        \resumeSubheading{Journal Articles \& Conference Proceedings}{}{}{}
            \resumeItemListStart
                \resumeItem{Anna Mataczynska, Michal Paprocki, \textbf{Jan Szczekulski} and Bartlomiej Kwiek. \textit{Laser Therapy of Cutis Marmorata Telangiectatica Congenita Vascular Malformation.} \textbf{Dermato}, volume 29 2023}
                \vspace{3pt}
                \resumeItem{\textbf{Jan Szczekulski}, Michal Paprocki, Ryan Butler, Anna Mataczynska and Bartlomiej Kwiek. \textit{Investigating the effectiveness of convolutional neural networks in predicting the efficacy rate of treating port-wine stain birthmark.} \textbf{Journal of Investigative Dermatology}, volume 143 2023}
                \vspace{3pt}
                \resumeItem{Michal Paprocki, Anna Mataczynska, \textbf{Jan Szczekulski} and Bartlomiej Kwiek. \textit{The effectiveness of cutis marmorata telangiectatica congenita laser therapy.} \textbf{Journal of Investigative Dermatology}, volume 143 2023}
                \vspace{3pt}
                \resumeItem{Michal Paprocki, Anna Mataczynska, \textbf{Jan Szczekulski}, and Bartlomiej Kwiek. \textit{Long term treatment of pws might require a new dual therapy consisting of induction and maintenance}. In 41st ASLMS Annual Conference on Energy Based Medicine\& Science, in San Diego California, USA.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{2}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item Graduate Networks Systems
                \item Object Oriented Programming
                \item Intro to Programming
                \item Advanced Computer Vision
                \item Computer Vision I
                \item Recommendation Systems
                \item Data Mining and Visualisation
                \item Statistics, Linear Algebra \& Calculus courses
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd

    
\end{document}
