%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Jan Szczekulski} \\ \vspace{3pt}
    \href{mailto:jszczekulski@ucsd.edu}{\raisebox{-0.2\height}\faEnvelope\  \underline{email}} ~ 
    \href{https://jan-cs.com/}{\raisebox{-0.2\height}\faGithub\ \underline{website}} ~
    \href{https://www.linkedin.com/in/jan-szczekulski-272ab615a}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin}}  ~
    \href{https://github.com/szczekulskij}{\raisebox{-0.2\height}\faGithub\ \underline{github}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {UC San Diego}{Sept. 2023 -- Present}
      {Master of Science in Computer Science}{San Diego, California}
    \resumeSubheading
      {University of Liverpool}{Sept. 2017 -- May 2020}
      {Bachelor of Science in Computer Science}{Liverpool, UK}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{2}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item Intro to Programming
                \item Object Oriented Programming
                \item Data Structures and Algorithms
                \item Complexity Of Algorithms
                \item Probabilistic Reasoning\&Learning
                \item Mathematical Models
                \item Statistical Theory And Methods I \& II
                \item Networks In Theory And Practice
                \item Applied Probability
                \item Applied Stochastic Models
                \item Mathematical Risk Theory
                \item Database Development
                \item Introduction to AI
                \item Advanced AI
                \item Data Mining and Visualisation
                \item Recommendation Systems
                
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {The Hut Group}{Dec. 2021 -- Aug. 2023}
      {Software Engineer}{Manchester, UK}
      \resumeItemListStart
        \resumeItem{I led the experimentable widgets project, which enabled the company to quickly and dynamically test changes to website's via A/B testing.}
        \resumeItem{As part of this project, I've made alterations to the larger internal architecture, including 4 core backends and 2 internal frontends. As of time of writing, this feature enabled 15 new A/B tests in only 2 months, all set up effortlessly via UI.}
        \resumeItem{Set up various CI/CD pipelines utilising shell, Jenkins, Docker \& Kubernetes}        
        \resumeItem{Mentored and led development of multiple juniors}        
      \resumeItemListEnd

    \resumeSubheading
      {The Hut Group}{Sept. 2020 -- Dec. 2021}
      {Graduate Data Scientist}{Manchester, UK}
      \resumeItemListStart
        \resumeItem{Helped develop a company-wide ML algorithm and accuracy metrics for short-term demand forecasting}
        \resumeItem{I conducted 7 A/B/n tests, and performed thorough data analyses which resulted in £1million rise in sales year-on-year. Two of the A/B tests included forecasting time-series data utilising ML}
        \resumeItem{Improved and automated manual tools surrounding internal A/B testing platform such as duration estimation, results generation or metrics addition. Improved and set up acceptance and integration testing for multiple components, and improved robustness of CI/CD pipelines.}
        \resumeItem{Built data pipelines from scratch, including setting up virtual machines, Jenkins, and periodic scripts.}
      \resumeItemListEnd


    \resumeSubheading
      {Lazarski University}{June 2021 -- Present}
      {Research Collaboration}{Warsaw, Poland}
      \resumeItemListStart
        \resumeItem{Worked on research concerning PWS birthmark malformation}
        \resumeItem{Conducted retrospective data analysis of the past treatments to determine the best treatment approach for PWS birtmarks}
        \resumeItem{Utilized CNNs and transfer learning to roughly predict the patient's treatment's results.}
      \resumeItemListEnd


      \resumeSubheading
      {University of Liverpool}{June 2020 -- Aug 2020; Aug 2022 - Aug 2023}
      {Research Assistant}{Liverpool, UK}
      \resumeItemListStart
        \resumeItem{Worked on finding ways to increase the efficiency of geometric reconstruction of nanowires through the application of Convolutional Neural Networks (CNNs)}
      \resumeItemListEnd


      
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Monet-me-this web app } $|$ \emph{Javascript, React, Java, Python, PyTorch, Linux}}{November 2022}
          \resumeItemListStart
            \resumeItem{I developed and launched a full-stack web application game where players must determine which images were generated by a famous painters and which by the AI.}
            \resumeItem{Implemented a Generative Adversarial Network (GAN) Artificial Intelligence (AI) model which can turn any photograph into a painting that closely resembles the style of the master painters such as Monet or Van Gogh.}
          \resumeItemListEnd 
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{AI application in tomography reconustruction} $|$ \emph{Python, Numpy, Tensorflow}}{August 2022}
          \resumeItemListStart
            \resumeItem{I conducted a research study to improve 3D nanowire reconstruction using Convolutional Neural Networks (CNNs).}
            \resumeItem{The CNNs were trained to determine optimal angles for accurate reconstructions, minimizing discrepancies between 2D polygons and their re-constructed 3D counterparts}
          \resumeItemListEnd
          \vspace{-13pt}
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, SQL, Java, Shell, JavaScript, HTML/CSS,  C++,} \\
     \textbf{Frameworks}{: PyTorch, Tensorflow, Pandas, Numpy, Matplotlib, React, Angular, SpringBoot} \\
     \textbf{Technologies/Tools}{: Git, GH actions, Docker, Jenkins, Kubernetes} \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Publications}
    \resumeSubHeadingListStart
        \resumeSubheading{Journal Articles}{}{}{}
            \resumeItemListStart
                \resumeItem{Anna Mataczynska, Michal Paprocki, \textbf{Jan Szczekulski} and Bartlomiej Kwiek. \textit{Laser Therapy of Cutis Marmorata Telangiectatica Congenita Vascular Malformation.} \textbf{Dermato}, volume 29 2023}
            \resumeItemListEnd
            \resumeItemListStart
                \resumeItem{\textbf{Jan Szczekulski}, Michal Paprocki, Ryan Butler, Anna Mataczynska and Bartlomiej Kwiek. \textit{Investigating the effectiveness of convolutional neural networks in predicting the efficacy rate of treating port-wine stain birthmark.} \textbf{Journal of Investigative Dermatology}, volume 143 2023}
            \resumeItemListEnd
            \resumeItemListStart
                \resumeItem{Michal Paprocki, Anna Mataczynska, \textbf{Jan Szczekulski} and Bartlomiej Kwiek. \textit{The effectiveness of cutis marmorata telangiectatica congenita laser therapy.} \textbf{Journal of Investigative Dermatology}, volume 143 2023}
            \resumeItemListEnd
    \resumeSubHeadingListEnd
    \resumeSubHeadingListStart
        \resumeSubheading{Conference Proceedings}{}{}{}
            \resumeItemListStart
                \resumeItem{Michal Paprocki, Anna Mataczynska, \textbf{Jan Szczekulski}, and Bartlomiej Kwiek. \textit{Long term treatment of pws might require a new dual therapy consisting of induction and maintenance}. In 41st ASLMS Annual Conference on Energy Based Medicine\& Science, in San Diego California, USA.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd
\end{document}
