%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Jan Szczekulski} \\ \vspace{3pt}
    \href{mailto:jszczekulski@ucsd.edu}{\raisebox{-0.2\height}\faEnvelope\  \underline{email}} ~ 
    \href{https://jan-cs.com/}{\raisebox{-0.2\height}\faGithub\ \underline{website}} ~
    \href{https://www.linkedin.com/in/jan-szczekulski-272ab615a}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin}}  ~
    \href{https://github.com/szczekulskij}{\raisebox{-0.2\height}\faGithub\ \underline{github}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {UC San Diego}{Sept. 2023 -- Present}
      {Master of Science in Computer Science}{San Diego, California}
    \resumeSubheading
      {University of Liverpool}{Sept. 2017 -- May 2020}
      {Bachelor of Science in Computer Science}{Liverpool, UK}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{2}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item Robotics and Autonomous Systems
                \item Object Oriented Programming
                \item Intro to Programming
                \item Introduction to AI
                \item Advanced AI
                \item Probabilistic Reason\&Learning
                \item Computer Vision I
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {The Hut Group}{Dec. 2021 -- Aug. 2023}
      {Software Engineer}{Manchester, UK}
      \resumeItemListStart
        \resumeItem{I led the experimentable widgets project, which enabled the company to quickly and dynamically test changes to website's via A/B testing.}
        \resumeItem{As part of this project, I've made alterations to the larger internal architecture, including 4 core backends and 2 internal frontends. As of time of writing, this feature enabled 15 new A/B tests in only 2 months, all set up effortlessly via UI.}
        \resumeItem{Set up various CI/CD pipelines utilising shell, Jenkins, Docker \& Kubernetes}        
        \resumeItem{Mentored and led development of multiple juniors}        
      \resumeItemListEnd

    \resumeSubheading
      {The Hut Group}{Sept. 2020 -- Dec. 2021}
      {Graduate Data Scientist}{Manchester, UK}
      \resumeItemListStart
        \resumeItem{Helped develop a company-wide ML algorithm and accuracy metrics for short-term demand forecasting}
        \resumeItem{I conducted 7 A/B/n tests, and performed thorough data analyses which resulted in £1million rise in sales year-on-year. Two of the A/B tests included forecasting time-series data utilising ML}
        \resumeItem{Improved and automated manual tools surrounding internal A/B testing platform such as duration estimation, results generation or metrics addition. Improved and set up acceptance and integration testing for multiple components, and improved robustness of CI/CD pipelines.}
        \resumeItem{Built data pipelines from scratch, including setting up virtual machines, Jenkins, and periodic scripts.}
      \resumeItemListEnd


    \resumeSubheading
      {Lazarski University}{June 2021 -- Present}
      {Research Assistant}{Warsaw, Poland}
      \resumeItemListStart
        \resumeItem{Worked on research concerning PWS birthmark malformation}
        \resumeItem{Conducted retrospective data analysis of the past treatments to determine the best treatment approach for PWS birtmarks}
        \resumeItem{Utilized CNNs and transfer learning to roughly predict the patient's treatment's results.}
      \resumeItemListEnd


      \resumeSubheading
      {University of Liverpool}{June 2020 -- Aug 2020; Aug 2022 - Aug 2023}
      {Research Assistant}{Liverpool, UK}
      \resumeItemListStart
        \resumeItem{Worked on finding ways to increase the efficiency of geometric reconstruction of nanowires through the application of Convolutional Neural Networks (CNNs)}
      \resumeItemListEnd


      
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Gym Reservation Bot} $|$ \emph{Python, Selenium, Google Cloud Console}}{January 2021}
          \resumeItemListStart
            \resumeItem{Developed an automatic bot using Python and Google Cloud Console to register myself for a timeslot at my school gym.}
            \resumeItem{Implemented Selenium to create an instance of Chrome in order to interact with the correct elements of the web page.}
            \resumeItem{Created a Linux virtual machine to run on Google Cloud so that the program is able to run everyday from the cloud.}
            \resumeItem{Used Cron to schedule the program to execute automatically at 11 AM every morning so a reservation is made for me.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Ticket Price Calculator App} $|$ \emph{Java, Android Studio}}{November 2020}
          \resumeItemListStart
            \resumeItem{Created an Android application using Java and Android Studio to calculate ticket prices for trips to museums in NYC.}
            \resumeItem{Processed user inputted information in the back-end of the app to return a subtotal price based on the tickets selected.}
            \resumeItem{Utilized the layout editor to create a UI for the application in order to allow different scenes to interact with each other.}
          \resumeItemListEnd 
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{Transaction Management GUI} $|$ \emph{Java, Eclipse, JavaFX}}{October 2020}
          \resumeItemListStart
            \resumeItem{Designed a sample banking transaction system using Java to simulate the common functions of using a bank account.}
            \resumeItem{Used JavaFX to create a GUI that supports actions such as creating an account, deposit, withdraw, list all acounts, etc.}
            \resumeItem{Implemented object-oriented programming practices such as inheritance to create different account types and databases.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, SQL, Java, C++, Shell, JavaScript, HTML/CSS, Prolog} \\
     \textbf{Frameworks}{: PyTorch, Tensorflow, Pandas, Numpy, Matplotlib, React, SpringBoot} \\
     \textbf{Technologies/Tools}{: Git, GH actions, Docker, Jenkins, Kubernetes} \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Publications}
    \resumeSubHeadingListStart
        \resumeSubheading{Journal Articles}{}{}{}
            \resumeItemListStart
                \resumeItem{Anna Mataczynska, Michal Paprocki, \textbf{Jan Szczekulski} and Bartlomiej Kwiek. \textit{Laser Therapy of Cutis Marmorata Telangiectatica Congenita Vascular Malformation.} \textbf{Dermato}, volume 29 2023}
            \resumeItemListEnd
            \resumeItemListStart
                \resumeItem{\textbf{Jan Szczekulski}, Michal Paprocki, Ryan Butler, Anna Mataczynska and Bartlomiej Kwiek. \textit{Investigating the effectiveness of convolutional neural networks in predicting the efficacy rate of treating port-wine stain birthmark.} \textbf{Journal of Investigative Dermatology}, volume 143 2023}
            \resumeItemListEnd
            \resumeItemListStart
                \resumeItem{Michal Paprocki, Anna Mataczynska, \textbf{Jan Szczekulski} and Bartlomiej Kwiek. \textit{The effectiveness of cutis marmorata telangiectatica congenita laser therapy.} \textbf{Journal of Investigative Dermatology}, volume 143 2023}
            \resumeItemListEnd
    \resumeSubHeadingListEnd
    \resumeSubHeadingListStart
        \resumeSubheading{Conference Proceedings}{}{}{}
            \resumeItemListStart
                \resumeItem{Michal Paprocki, Anna Mataczynska, \textbf{Jan Szczekulski}, and Bartlomiej Kwiek. \textit{Long term treatment of pws might require a new dual therapy consisting of induction and maintenance}. In 41st ASLMS Annual Conference on Energy Based Medicine\& Science, in San Diego California, USA.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd
\end{document}
